Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-11-27 leadership_across_cultures_contexts.Rmd
Also moved table captions into "caption" arg in kable.

```{r qualfuncvars, echo=FALSE, message=F, warning=FALSE, eval=F}
library(readr)
qual_func_var_tab<-read_csv('func_qual_definitions.csv', na = 'NA')
library(knitr)
kable(qual_func_var_tab, caption = "Operational definitions for coded leader qualities and functions.")
```

@@

```{r costbenefitvars, echo=FALSE, message=F, warning=FALSE, eval=F}
library(readr)
cost_benefit_vars_tab<-read_csv('costs_benefits.csv', na = 'NA')
library(knitr)
kable(cost_benefit_vars_tab, caption = "Operational definitions for coded benefits and costs for leaders and followers.")
```

>>>>

```{r qualfuncvars, echo=FALSE, message=F, warning=FALSE}
library(readr)
qual_func_var_tab<-read_csv('func_qual_definitions.csv', na = 'NA')
library(knitr)
kable(qual_func_var_tab, caption = "Operational definitions for coded leader qualities and functions.")
```

@@

```{r costbenefitvars, echo=FALSE, message=F, warning=FALSE}
library(readr)
cost_benefit_vars_tab<-read_csv('costs_benefits.csv', na = 'NA')
library(knitr)
kable(cost_benefit_vars_tab, caption = "Operational definitions for coded benefits and costs for leaders and followers.")
```
